### 2020-11-10 Reports/JOURNAL - Confidence Regions/Chapters/relatedWork.tex

\section{Entropy-Complexity plane in the literature}

The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps~\cite{rosso2013characterization, xiong2020complexity, olivares2012contrasting}.
However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization~\cite{larrondo2002statistical, gonzalez2005statistical}.

>>>>

\subsection{Entropy-Complexity plane in the literature}

The first works on the characterization of white noises with permutation entropy arose from the need to discriminate them in relation to chaotic maps \citep{rosso2013characterization,olivares2012contrasting, xiong2020complexity}.
However, it was found that the measure of statistical complexity was able to efficiently quantify the performance of pseudorandom number generators, expanding the possibilities of using information theory descriptors with the Bandt-Pompe symbolization \citep{larrondo2002statistical, gonzalez2005statistical}.
